\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Collapse a layer of hierarchy in sec:qualitative.

\section{Qualitative Analysis of the Existing Interface (Study 1)}
We performed qualitative research as an exploratory effort to gain an 
understanding of underlying problems, such as reasons for confusion 
during the configuration process and motivations for particular choices in 
configuration. We did this through observing each participant as they 
interacted with Tor Browser 5.0.3 interface and interviewed them about
their experience. This study provides insights into particular problems with 
the current Tor Browser configuration interface, and helps us to design
a new interface which addresses these problems and gives foundation
for hypotheses to test in quantitative research.

\subsection{Methodology} 
In this section, we talk about the details of our qualitative user study, such as the inspection of the interface, censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.

\subsubsection{Inspection} 
A combination of usability inspection methods~\cite{nielsen1994usability}
were used to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, feature inspection was performed to list sequences
of features used to accomplish typical tasks, taking note of long sequences or cumbersome
steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
that may cause confusion for users during our study.

\subsubsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our qualitative and quantitative user studies. \\

@@

\subsubsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 5 participants for each censorship environment.
We pre-screened ~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simluated censorship environment for our summative
usability test~\cite{summative}.

@@

\subsubsection{Procedure}
We conducted a qualitative evaluation of the interface through real-time observations of 
users interacting with the configuration interface in a simulated censored environment.
There was no researcher-user interaction during the experiment. A follow-up interview 
detailed their thoughts about the configuration process.

>>>>

\section{Qualitative Analysis of the Existing Interface (Study 1)}
\label{sec:qualitative}

We performed qualitative research as an exploratory effort to gain an 
understanding of underlying problems, such as reasons for confusion 
during the configuration process and motivations for particular choices in 
configuration. We did this through observing each participant as they 
interacted with Tor Browser 5.0.3 interface and interviewed them about
their experience. This study provides insights into particular problems with 
the current Tor Browser configuration interface, and helps us to design
a new interface which addresses these problems and gives foundation
for hypotheses to test in quantitative research.

\subsection{Inspection}
A combination of usability inspection methods~\cite{nielsen1994usability}
were used to prepare for the user study. Two researchers conducted a pluralistic 
walkthrough and stepped through various censorship
scenarios, discussing which elements would be involved for that use case, and walking 
through the configuration process. After compiling all the possible paths through the 
interface, feature inspection was performed to list sequences
of features used to accomplish typical tasks, taking note of long sequences or cumbersome
steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
that may cause confusion for users during our study.

\subsection{Setup}
\label{sec:setup}
We simulated three censorship environments for our qualitative and quantitative user studies. \\

@@

\subsection{Recruitment}
Using established practices from the field of user experience research~\cite{howmanyusers},
we recruited 5 participants for each censorship environment.
We pre-screened ~\cite{screening} our participants for diversity of gender, age, technical expertise,
and self-reported familiarity with Tor in each simluated censorship environment for our summative
usability test~\cite{summative}.

@@

\subsection{Procedure}
We conducted a qualitative evaluation of the interface through real-time observations of 
users interacting with the configuration interface in a simulated censored environment.
There was no researcher-user interaction during the experiment. A follow-up interview 
detailed their thoughts about the configuration process.
